\begin{acknowledgments}

I would like to place my foremost and deepest gratitude to my supervisor, Distinguished Professor Beng Chin Ooi. 
Thank you for your guidance throughout my PhD years. 
In the early years when I feel lost from time to time, it is Professor Ooi who tirelessly tolerates my naughtiness and guides me out of uncertainties. 
In retrospect, this tough period has made a profoundly positive impact on my self-developments.

Two heads are better than one. This thesis is inseparable from the efforts of my collaborators. 
Chapter~\ref{ch:twin} is the joint work with Gang Chen, Tien Tuan Anh Dinh, Qian Lin, Dumitrel Loghin, and Meihui Zhang. 
Chapter~\ref{ch:prov} is collaborated with Gang Chen, Tien Tuan Anh Dinh, and Qian Lin. 
Chapter~\ref{ch:txn} is a result of the contribution from Dumitrel Loghin, Quang-Trung Ta, Meihui Zhang, and Gang Chen.
Chapter~\ref{ch:view} is born through cheering discussions with Yaron Kanza, and Divesh Srivastava from AT\&T Labs-Research.
I would like to take this opportunity to thank the above co-authors, which offer me abundant tips to conduct first-class research. 

It is also my privilege to work with my seniors, Luo Zhaojing, Zheng Kaiping, Xie Zhongle, Wang Ji, Ji Xin, and my fortune to grow with my peers, Cai Shaofeng, Feng Piaopiao. 
% TODO: add examiners
% I would also like to say thanks to my thesis committee members, Chee Yong Chan and Yong Meng Teo, for their valuable feedback on this thesis. 

Doing PhD is hard. I still remember the tough time when I set out the PhD voyage. Every day buried under hundreds of papers, it is easy to become frustrated at my research direction and then the desperation looms. 
Things turn around in my third year when my first publication wins the VLDB 2019 Best Paper Award. This award boosts my confidence and reassures myself that the previous efforts pay off. 
And in next two years, I, as the first author, continuously made two publications on ACM SIGMOD, the top-tiered database conference.
Beyond the technical knowledge and research skill, this is the most valuable lesson from my PhD journey: no achievements accomplish at one stroke but they will definitely spur with long accumulation.  
And I would like to share this wisdom of life with all my dear readers of this thesis, especially to those junior PhD candidates. 

Last but not the least, I never forget the continuous support from my family. For my parents, sorry for being even grumpier than normal, especially at the starting stage. For my wife, Junna, I love you more than you can imagine. This thesis is dedicated to you and our bright future. 
    

\end{acknowledgments}
